\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-09-17 parts-tr2global.tex
update

\todo{this statement is too strong if we consider intervals, but correct if we are not}
It results that deriving Thomas specification for dynamics of a PH model
requires that every sort converges toward a unique focal process, i.e., that every sort has a
deterministic behaviour w.r.t. any context, as stated by \pref{pro:deterministic-sort}.

@@

\todo{examples}

>>>>

From \pref{def:focals}, we call a \emph{deterministic sort} \pref{pro:deterministic-sort} a sort $a$
that has a single focal process for any possible configuration of its predecessors in the scope of
$L_a$.

@@

\todo{examples?}

For the inference of the interaction graph and Thomas parameters from a PH model, the following
sections assume that \emph{all the cooperative sorts are deterministic}.
\todo{add more explanation depending on the text of the next sections}
